Proposed Solution

### 2016-01-29 system.tex
random

For a given value, its quantum type is updated over time. When the

At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.

This idea is closely related to existentially quantified types.

>>>>

For a given value, its quantum type is updated over time. When the type inference uniquely determines the type, the probability of all other types is set to zero, and  the associated rules are withdrawn.

This idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
